So you've decided to detonate helium

### 2020-05-07 sdc_applications/paper.tex
some notes

@@

@@

@@

>>>>

\subsection{Reaction Convergence}

@@

aprox13 flames

simplified-SDC takes 3x more timesteps than Strang

look at number of right hand side calls

@@

\subsection{Massive Star}

we need to look at the number of RHS calls spatially

also need to look at tolerances in the burner

analytic Jacobian run is much faster

what does Strang run do

\subsection{X-ray bursts}

crashed with too many subcycles.  Need to rerun with new Jacobian

@@

it doesn't run more than a few steps with simplified SDC

has a small density error and too many subcycles after ~ 128 steps
